### 2023-09-26 paper/draft.tex
unit test for AURC def 2

\begin{itemize} %tailor to audience
    \item $f(x)_{k+1}$: write out with $g$, as it is restrictive to have this additional output in $[0,1]$, can be in $\mathbb{R}$; can have its own parameters and features
    \item Sanity check complete
    \item Differentiability: 1) indicator function, 2) comparison (>)
\end{itemize}

% \section{Example \AURC}

@@

For \DC{}, we benchmark results on both \tobacco{} (original train-val-test splits 800-200-2482) and \rvl.  
We also created a subsampled student training set, \rvlone, by randomly selecting 1K training images per class from \rvl. The originally large training size hinders experimentation (longer iteration cycles).
By evaluating the full \rvl{} test set, we provide a fair evaluation of the usefulness of KD methods, while avoiding the cumbersomeness of student fine-tuning on a large dataset. Additionally, we evaluate RVL-CDIP-N, which is a test set created for testing robustness to covariate shifts.

>>>>

\begin{itemize} %tailor to audience
\item $f(x)_{k+1}$: written as $g$, as it is restrictive to have this additional output in $[0,1]$, can be in $\mathbb{R}$; can have its own parameters (e.g., MLP) with features derived from any intermediate representation of $x$
\item Sanity check complete: naive and matrix version
    \item Differentiability: 1) indicator function, 2) comparison (>)
\end{itemize}
% \section{Example \AURC}

@@

For \DC{}, we benchmark results on both \tobacco{} (original train-val-test splits 800-200-2482) and \rvl.  
We also created a subsampled student training set, \rvlone, by randomly selecting 1K training images per class from \rvl. The originally large training size hinders experimentation (longer iteration cycles).
By evaluating the full \rvl{} test set, we provide a fair evaluation of the usefulness of KD methods, while avoiding the cumbersomeness of student fine-tuning on a large dataset. Additionally, we evaluate on RVL-CDIP-N, which is a test set created for testing robustness to covariate shifts.
